The Aquarius Stream Progenitor Was Not A Globular Cluster: \\ Its History is Far More Interesting

### 2012-12-04 2012-aqs/draft-aqs.tex
Updated plots + captions

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
	\caption{Line velocity measurements.}
	\label{fig:line-velocities}
\end{figure}

@@

The equivalent widths for all transitions were measured automatically using software for this study. Given the rest wavelength and an initial guess of the FWHM, a Gaussian function is iteratively fitted to the absorption profile. At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial. Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements. Any group of pixels that deviate significantly ($>2\sigma$) to the local continuum are cosmic ray hits, or more likely trough points of a neighbouring profile. We attempt to fit a Gaussian profile to each of these groups of deviating pixels, using the best estimate of the local continuum. If a profile is successfully fitted, then all points belonging to that profile are excluded from the continuum determination. When fitting Gaussian profiles, the $\chi^2$ difference between the observation and the profile is minimized. In order to account for blended transitions, our $\chi^2$ function is weighted based on the distance to the rest wavelength. Pixels near the rest wavelength are weighted higher than those on the wings. Although this approach relies on an accurate ($<4$\,km s$^{-1}$) radial velocity correction, it greatly improves the accuracy of the equivalent width measurements.

We note that the results of our iterative fitting approach are entirely insensitive to the initial FWHM guess. Increasing the initial guess from 0.1\,\AA{} to 1 or 2\,\AA{} -- an unphysical large value for high-resolution spectra -- does not alter our equivalent width measurements. Only a small increase in computational cost is observed. Although we are confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality.

@@

% equivalent widths plot with Norris for HD 122563
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
	\caption{The gold standard comparison.}
	\label{fig:ew-compare}
\end{figure}

@@

>>>>

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for the doppler shift with our cross-correlation measurement. The mean residual velocity is within our uncertainties derived from cross-correlation.}
	\label{fig:line-velocities}
\end{figure}

@@

The equivalent widths for all transitions were measured automatically using software for this study. Given the rest wavelength and an initial guess of the FWHM, a Gaussian function is iteratively fitted to the absorption profile. At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial. Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements. Any group of pixels that deviate significantly ($>2\sigma$) to the local continuum are cosmic ray hits, or more likely trough points of a neighbouring profile. We attempt to fit a Gaussian profile to each of these groups of deviating pixels, using the best estimate of the local continuum. If a profile is successfully fitted, then all points belonging to that profile are excluded from the continuum determination. When fitting Gaussian profiles, the $\chi^2$ difference between the observation and the profile is minimized. In order to account for blended transitions, our $\chi^2$ function is weighted based on the distance to the rest wavelength. Pixels near the rest wavelength are weighted higher than those on the wings. Although this approach relies on a reasonably accurate ($<4$\,km s$^{-1}$) radial velocity correction, it greatly improves the accuracy of the equivalent width measurements.

We note that the results of our iterative fitting approach are entirely insensitive to the initial FWHM guess. Increasing the initial guess from 0.1\,\AA{} to 1 or 2\,\AA{} -- an unphysical large value for high-resolution spectra -- does not alter any of our equivalent width measurements. Only a small increase in computational cost is observed. Although we are confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality.

@@

% equivalent widths plot with Norris for HD 122563
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
	\caption{A comparison showing equivalent widths measured for HD140283 using an automatic routine (see \S\ref{sec:line-measurements}), and those found with careful hand measurements by \citet{norris;et-al_1996}. No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda = -0.64 \pm 2.78$ m\AA{}.}
	\label{fig:ew-compare}
\end{figure}

@@

% [alpha/Fe]
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/aquarius-alpha-fe.pdf}
	\caption{A plot showing $[\alpha/\mbox{Fe}]$ for all Aquarius stream stars.}
	\label{fig:alpha-fe}
\end{figure}

% Mg-Al
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/aquarius-mg-al.pdf}
	\caption{A plot showing [Mg/Al] for all Aquarius stream stars.}
	\label{fig:mg-al}
\end{figure}

% [Na/Fe], [Cr/Fe], [Ni/Fe]
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/aquarius-na-cr-ni-fe.pdf}
	\caption{A plot showing [Na/Fe], [Cr/Fe], and [Ni/Fe] for all Aquarius stream stars.}
	\label{fig:na-cr-ni-fe}
\end{figure}

% [Na/Fe], [Ni/Fe]
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/aquarius-na-ni.pdf}
	\caption{A plot showing [Na/Fe] and [Ni/Fe] for all Aquarius stream stars.}
	\label{fig:na-ni}
\end{figure}

% [O/Fe], [Na/Fe]
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/aquarius-o-na.pdf}
	\caption{A plot showing [O/Fe] and [Na/Fe] for all Aquarius stream stars.}
	\label{fig:o-na}
\end{figure}

% Toombre
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/plot-toombre.pdf}
	\caption{Toombre plot.}
	\label{fig:toombre}
\end{figure}
